Developing a preprint culture in biology

### 2012-10-05 ms.tex
PeerJ uses CC-BY not CC-BY-SA see https://peerj.com/FAQ/#license
Minor edits to Fac1000 and Conclusions sections

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free and a onetime
(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
preprints. It is also worth noting that the preprint server is not tied to the
journal, so preprints can be posted regardless of where they will eventually be
submitted for publication.

PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
need a license identical to the license that governs the original work.

@@

F1000Research is not a public preprint server like the previous three servers.
Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
without having it reviewed, papers submitted to F1000Research will eventually
be reviewed. Thus, F1000Research offers a hybrid model with publicly available
manuscripts at time of submission and standard peer-reviews. Manuscripts are
considered ``accepted'' and will only be indexed after two positive referee
response. F1000Research works closely with data providers to integrate raw
data to the paper. Forinstance, upon submitting a paper, authors are asked to
upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
the DOI of which are given in the paper when the data are first mentionned.
The licensing of the data is similar to the one used by FigShare, meaning that
the articles are free to access, and can be redistributed readily. By putting
much effort in integrating data to the paper, F1000Research is working to make
science more reproducible and open.

@@

Open preprint servers offer a great opportunity for open science, especially if
the community embraces the idea of discussing preprints. Initiatives like
Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
new blog discussing arXiv papers in population genetics, will help make arXiv
attractive for scientists looking to promote their work. These initiatives are
important to fully exploit the potential of open preprints servers. Posting
preprints online increases the community of available informal peer reviewers,
and uses the internet for its original community-building purposes.

>>>>

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free and a onetime
(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
preprints. It is also worth noting that the preprint server is not tied to the
journal, so preprints can be posted regardless of where they will eventually be
submitted for publication. PeerJ uses the same CC-BY license used by Figshare.

@@

F1000Research is not a public preprint server like the previous three servers.
Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
without having it reviewed, papers submitted to F1000Research will eventually
be reviewed. Thus, F1000Research offers a hybrid model with publicly available
manuscripts at time of submission and standard peer-reviews. Manuscripts are
considered ``accepted'' and will only be indexed after two positive referee
response. F1000Research works closely with data providers to integrate raw
data to the paper. For instance, upon submitting a paper, authors are asked to
upload their data, which are then integrated in \emph{e.g.} figshare widgets,
the DOI of which are given in the paper when the data are first mentionned.
The licensing of the data is similar to that used by FigShare, meaning that
the articles are free to access, and can be redistributed readily. By
integrating data to the paper, F1000Research is working to make
science more reproducible and open.

@@

Open preprint servers offer a great opportunity for science, especially if
the community embraces the idea of openly discussing preprints. Initiatives like
Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
new blog discussing arXiv papers in population genetics, will help make arXiv
attractive for scientists looking to promote their work. These initiatives are
important to fully exploit the potential of open preprints servers. Posting
preprints online increases the community of available informal peer reviewers,
and uses the internet for its original community-building purposes.
